Supplementary Information

### 2021-06-01 doc/manuscript/ForestGEO_treerings_SI.Rmd
fix fig legend errors

RW_interactions_all_legend = "Figure S56. All signficant climate - DBH interactions with RW as the response metric."
BAI_interactions_all_legend ="Figure S57. All signficant climate - DBH interactions with RW as the response metric."

>>>>

RW_interactions_all_legend = "Figure S56. All significant climate - DBH interactions with RW as the response metric."
BAI_interactions_all_legend ="Figure S57. All significant climate - DBH interactions with BAI as the response metric."
